Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-02-09 ribose-paper.RMD
small updates to discussion, needs alot more work

The main findings of the present study were that exercise training with glucose for five sessions did not affect muscle biology markers, measured as total RNA and -protein, rRNA and specific protein, compared to RT with placebo. Similarly, RT with glucose did not affect markers of muscle functionality such as muscular recovery, total session volume, and training intensity, compared to RT with placebo. There are several studies suggesting high glucose treatment is important to markers of ribosome biogenesis (MARIAPPAN11, TANAKA18, ZHAI12), however, the perspective of exogenous glucose ingestion combined with RT on subsequent adaptations have remained unexplored. As a result, our hypotheses and purposes were quite exploratory and, considering previous suggestions, it is interesting that we did not observe any difference between RT with glucose and RT with placebo on the aforementioned markers of ribosome biogenesis.

To our knowledge, no previous study has investigated the effects of glucose compared to placebo ingestion with RT on ribosome biogenesis in human skeletal muscle cells. Through recent studies, the current model of ribosome biogenesis suggests that changes in the accumulation of total RNA and rRNA early after the onset of an RT-period predict long-term responses in RT adaptation (FIGUEIREDO19). Therefore, the lack of effects of glucose on total RNA and rRNA after two weeks of moderate volume RT do indicate that glucose per se does not induce positive long-term adaptations in muscle growth. First, the time frame of the intervention has previously served as a predictor of long-term responses, as recent studies have shown augmentation of ribosome biogenesis by total RNA and rRNA following multiple sessions of RT (FIGUEIREDO16; HAMMARSTROM20). Figueiredo et al. (2016) observed increases in 47S pre-rRNA measurable after a single RT session, passing baseline after 4hrs, peaking at 24hrs and remaining elevated until 48hrs post-exercise. Other mature rRNA where first measurable after multiple sessions (FIGUEIREDO16). In addition, Hammarström et al. (2020) demonstrated that the most prominent augmentation in ribosome biogenesis markers occurred 2 weeks following moderate-volume unilateral RT. Secondly, translational capacity is now regarded a vital factor in long-term RT-induced adaptations (IS IT?), as increased ribosome content provides a higher basal MPS, giving regulation of ribosome biogenesis a central role in muscle growth (FIGUEIREDO19). This is further substantiated by the association between blunted ribosome biogenesis and poor responses to RT (HAMMARSTROM20; STEC16), in addition to the lack of relationship between translational efficiency and long-term gains in skeletal muscle mass (FIGUEIREDO19). Hence, two weeks of moderate-volume unilateral RT should have been sufficient to elicit differences between exercise training with glucose and placebo. Supporting the notion that our intervention indeed was effective, we observed expected augmentation in accumulation of total RNA and expression of rRNA (CITE THIS?). As there were no differences in total RNA and rRNA between exercise training with glucose and placebo in the present study, it is therefore reasonable to suggest that there were no differences in ribosome biogenesis by proxy. Further, since glucose did not augment ribosome content after two weeks of RT compared to placebo, it is unlikely that glucose per se is beneficial to long-term adaptations in RT.

>>>>

The main findings of the present study were that resistance training with glucose for five sessions did not affect muscle biology markers, measured as total RNA and -protein, rRNA and specific protein, compared to RT with placebo. Similarly, RT with glucose did not affect markers of skeletal muscle functionality such as muscular recovery, total session volume, and training intensity, compared to RT with placebo. There are studies suggesting that high glucose treatment impacts ribosome biogenesis in … cells (MARIAPPAN11; ZHAI12; TANAKA15), however, this effect does not seem to translate to human skeletal muscle cells in vivo.

To our knowledge, no previous study has investigated the effects of glucose compared to placebo ingestion with RT on ribosome biogenesis in human skeletal muscle cells, making our hypotheses exploratory and comparisons not straight forwards. The current model of ribosome biogenesis suggests that changes in the accumulation of total RNA and rRNA early after the onset of an RT period predict long-term RT adaptations (FIGUEIREDO19; HAMMARSTROM20; HAMMARSTROM21).Therefore, we assumed 2 weeks to be a suitable time frame for a moderate RT volume to elicit changes in ribosome biogenesis, as similar observations have been made previously (FIGUEIREDO16; HAMMARSTROM20; HAMMARSTROM21). In Hammarström et al. (2020), untrained participants that increased ribosome biogenesis after two weeks (5 RT sessions) of RT, also responded well after the entire intervention (12 weeks, 31 sessions). Figueiredo and colleagues (2016) also observed markedly acute effects in RT-untrained individuals, where 47S pre-rRNA increased after a single RT session, passing baseline after 4hrs, peaking at 24hrs and remaining elevated until 48hrs post-exercise. The four mature rRNA did not measurably increase until after multiple sessions (FIGUEIREDO16). As such, increases in total RNA and rRNA observed in the present study are in line with previous observations (FIGUEIREDO16; HAMMARSTROM20; H21?). Further, the accumulation of total RNA and rRNA is also suggested to reach a plateau after approximately 5 RT-sessions, thus, in addition to the demanding RT- and dietary protocol and the exploratory nature of the hypotheses, we did not conduct a more long-term intervention. COMMENT ON PROTEIN DATA HERE?

As we did not observe any effect of ingesting glucose before and after RT compared to placebo in this design, there is little to suggest that glucose *per se* has any additional effect on ribosome biogenesis, as long as the daily energy intake is sufficient to support cellular energy levels required to drive this process. Looking at previous observations from *in vitro* studies of rodents, yeast, and non-muscle cell cultures (MARIAPPAN11; KIM13; TANAKA18; ZHAI12; HOPPE09; MURAYAMA08), one interesting notion would be how low-carb or glucose starvation would affect ribosome biogenesis in human skeletal muscle cells...

..Secondly, translational capacity is now regarded a vital factor in long-term RT-induced adaptations (IS IT?), as increased ribosome content provides a higher basal MPS, giving regulation of ribosome biogenesis a central role in muscle growth (FIGUEIREDO19). This is further substantiated by the association between blunted ribosome biogenesis and poor responses to RT (HAMMARSTROM20; STEC16), in addition to the lack of relationship between translational efficiency and long-term gains in skeletal muscle mass (FIGUEIREDO19). Hence, two weeks of moderate-volume unilateral RT should have been sufficient to elicit differences between exercise training with glucose and placebo. Supporting the notion that our intervention indeed was effective, we observed expected augmentation in accumulation of total RNA and expression of rRNA (CITE THIS?). As there were no differences in total RNA and rRNA between exercise training with glucose and placebo in the present study, it is therefore reasonable to suggest that there were no differences in ribosome biogenesis by proxy. Further, since glucose did not augment ribosome content after two weeks of RT compared to placebo, it is unlikely that glucose per se is beneficial to long-term adaptations in RT.
